Self-assembly of colloid-cholesteric composites provides a possible route to switchable optical materials

### 2014-03-21 papers/2012-sandwich/CholColloids.tex
Second reply
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2351 40876441-3496-0410-a613-a2fca35b2ae2

But one may also choose to disperse colloidal particles in a cholesteric, 
rather than nematic, liquid crystal. The molecules making up this material are
chiral, and this causes their average orientation (described by a director field) to rotate in space in
a helical fashion, rather than remain uniform as in nematics. 
This typically creates a 1-dimensional periodic structure, called the cholesteric phase, whose wavelength 
is the pitch, $p$. The periodicity can however become fully three dimensional in the so-called blue phases (BPs)~\cite{mermin}. BPs arise because the director field can twist around more than one direction at once (see 
the cartoon in Supplementary Fig.~1). Such double twist 
regions (generally cylinders) are energetically favoured at high enough molecular chirality, but
lead to geometric frustration because it is impossible to tile the whole 3D
space with double twist cylinders without also introducing ``disclination lines'' 
(These are singular topological defects on which the director field is 
undefined.) In blue phases these disclination lines themselves either form a 3D periodic regular lattice (in so called BPI and BPII), or remain disordered (BPIII)~\cite{bp3}. 
%
BPs are stabilised by the tendency of chiral molecules to twist, but destabilised by the cost of forming topological defects (which locally diminish the molecular alignment). In conventional cholesteric materials~\cite{mermin} this balance is only achievable in a narrow temperature range of a few degrees, around the onset of liquid crystalline ordering.
\textcolor{red}{
However, recent advances in formulation have widened this stability
range enormously~\cite{kikuchi,bplasers,coleswidetrange,bpdevice}. Most
recently, templated BPs with a stability range of -125
to~125$^\circ$C have been reported \cite{coles}, paving the way to
applications of BPs in operational display devices.}

@@

\textcolor{red}{
The simulations presented here are representative of a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a diameter of around 50~nm. The simulations
address both the bulk structure, and the structure which forms when
the colloidal dispersion is confined in a narrow sandwich of width
comparable to the unit cell size~\cite{extrareference2}. It is seen
that a wide variety of structure is possible, and may be influenced
by parameters including the solid volume fraction, and the details
of the anchoring at the colloid surface (and the at the surface of the
confining walls). Further, evidence is found for metastable switching of
this structure in an applied electric field. Details of the
computational approach are set out in the Methods section, while
simulation parameters are reported in the Supplementary Information.
}

@@

\noindent
\textbf{Structure in bulk BPI.}
We show in Fig.~1 A-D the final state structures of four simulations in which we first equilibrated a stable BPI disclination network in bulk (with periodic boundary conditions) and then dispersed colloidal particles at random within it. Among dimensionless control parameters are the particle solid volume fraction $\phi$  ($\phi = 1\%$ or $5\%$); the ratio $r = R/\lambda$ of particle radius to the BP lattice parameter $\lambda$ (here $r\simeq 0.14$) and the ratio $w = WR/K$ where $W$ is the anchoring strength of the cholesteric at the particle surface, and $K$ is the elastic constant of the liquid crystal.
\textcolor{red}{
The anchoring strength is defined such that $W > 0$ imparts a preferred
orientation to the director field at the particle surface. This orientation
can be either normal to the surface or in a plane tangential to the surface,
a property related to surface chemistry in experimental systems.% but which
%can be imposed at will in simulations.
We choose} $w = 0.23, 2.3$ which are within typical experimental range~\cite{tiffany}. This parameter can be viewed as the ratio of the anchoring energy, $WR^2$, to the elastic energy scale for distortion~$KR$.

@@

As colloidal-nematic composites~\cite{tiffany}, all the structures in
Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloidal-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.
\textcolor{red}{
This figure is consistent with an estimate obtained by comparing
the mechanical properties of the network of defects stabilised by
colloidal particles with those of rubber~\cite{ramos} for
the relevant simulation parameters (see Supplementary Information).}

@@

@@

\textcolor{red}{
The degree of similarity between
the bulk and confined structures is somewhat masked by the local
change in particle density in the confined case. If one allows for
this, Figs.~1 and~2 show the individual structural motifs are actually
rather similar: templated lines for weak anchoring and clusters for
strong anchoring.
}

\medskip
\noindent
\textbf{Switching in electric field.}
An interesting question, relevant for applications to devices, is whether 
these structures can be modified, or switched, with electric fields.
Fig.~3 addresses this question, starting from amorphous Blue Phase III,
this time at a higher chirality. Dispersing colloidal particles in this
network
results in the particle occupying the available nodes, where the order
parameter is low (Fig.~3A; Supplementary Movie~5). Applying a high enough
field 
along the $x$ direction leads to a switching to a new phase, where colloidal 
arrays fit within a network with distorted hexagonal cells (Fig.~3B 
and Supplementary Fig.~7; Supplementary Movie~6). 
Remarkably, upon field removal this honeycomb structure does not find its 
way back to the 
configuration before switching on the field, but gets stuck into a metastable 
structure (Supplementary Fig.~7), with residual anisotropy along the field
switching 
direction. Cycling the field along the $x$ and $y$ directions leads to
distinct metastable structures, which are retained after field removal
(Supplementary Fig.~8 and Fig.~9).

@@

\textcolor{red}{
How do these simulations relate to experiment? Several authors have
used nanoparticles in the context of stabilising BPs
\cite{yoshida2009,karatairi}. These
nanoparticles are typically a few nanometres in size, in which case
stabilisation is explained by the mechanism of defect removal.
Experiments suggest this mechanism is also
relevant for larger particles in the range of 40--70~nm 
\cite{dierking}, which is consistent with the current simulations.
However, the mechanism is observed to be less efficient for
particles above 100~nm, where particles may start to disrupt
longer-range liquid crystal order \cite{dierking}. While the field of
self-assembly with nanoparticles is relatively new \cite{draper},
nanoparticles have also been used in both nematic \cite{milette2012}
and chiral liquid crystals \cite{cordoyiannis} as host fluid templates.
The variation of structure seen
in our simulations suggest that some careful characterisation of parameters
such as surface anchoring of particles (which are often stabilised, or even
functionalised with surface ligands), together with those associated
with any confining surfaces or interfaces, is required to understand the
final structure and to be able to reproduce it with a given experimental
protocol. The identification of a model system which could allow
unambiguous comparison between experimental systems and simulation
would be extremely useful. Such a system might adopt particles of
diameter in the range 50~nm or above, which allows a coarse-grained simulation
approach of the type used here to be adopted, which can then capture the
large-scale structure required to compare with experiment. In the same vein,
detailed surface chemistry is difficult to represent in coarse-grained
simulations, so heavily functionalised particles might be avoided.
}

@@

\medskip
\noindent
\textbf{Surface free energy.}
In addition to the fluid free energy density $f(Q_{\alpha\beta})$, a surface
free energy density is also present to represent the energetic cost of
anchoring at a solid surface. If the preferred order parameter tensor
at the solid surface is $Q^0_{\alpha\beta}$, then the surface free energy
density (per unit area) is
\begin{equation}
f_s(Q_{\alpha\beta}, Q^0_{\alpha\beta})
= {\textstyle \frac{1}{2}}W(Q_{\alpha\beta} - Q^0_{\alpha\beta})^2,
\end{equation}
where $W$ is a constant determining the strength of the anchoring.
The determination of $Q^0_{\alpha\beta}$ for normal and planar anchoring is
discussed below. For a colloidal particle of radius $R$, the strength of
the surface
anchoring compared which the bulk fluid elastic constant may be quantified
by the dimensionless parameter $WR/K$. For small values of this parameter,
the presence of a particle surface should have little impact on the local
fluid LC ordering.

@@

\bibitem{mermin} Wright, D.C., and Mermin, N.D.,
Crystalline liquids: the blue phases, {\it Rev. Mod. Phys.} {\bf 61},
\textcolor{red}{385--432} (1989).

@@

\bibitem{extrareference1}
\textcolor{red}{Ravnik, M., Alexander, G.P., Yeomans, J.M., and Zumer, S.,
Mesoscopic modelling of colloids in chiral nematics,
{\it Faraday Discuss.} {\bf 144}, 159--169 (2010).}

@@

\bibitem{extrareference2}
\textcolor{red}{Ravnik, M., Fukuda, J.-I.,  Yeomans, J.M., and Zumer, S.,
Confining blue phase colloids to thin layers,
{\it Soft Matter} {\bf 7}, 10144--10150 (2011).}

@@

\bibitem{ramos} 
\textcolor{red}{
Ramos, L., Zapotocky, M.,  Lubensky, T.C., and  Weitz, D.A.,
Rheology of defect networks in cholesteric liquid crystals,
{\it Phys. Rev. E} {\bf 66} 031711 (2002).}

@@

\textcolor{red}{
\bibitem{yoshida2009}
Yoshida, H., et al.,
Nanoparticle-stabilized cholesteric blue phases,
\textit{Appl. Phys. Express}, \textbf{2}, 121501 (2009).
%
\bibitem{karatairi} Karatairi, E., et al.,
% E. Karatairi, B. Ro\v{z}i\v{c}, Z. Kutnjak, V. Tzitzios, G. Nounesis,
% G. Cordoyiannis, C. Glorieux, J. Thoen, S. Kralj,
Nanoparticle-induced widening of the temperature range of
liquid-crystalline blue phases, 
\textit{Phys. Rev. E} \textbf{81}, 041703 (2010).
%
%\bibitem{rozic} B. Ro\v zi\v c,
% B. Ro\v{z}i\v{c}, V. Tzitzios, E. Karatairi, U. Tkalec, G. Nounesis,
% Z. Kutnjak, G. Cordoyiannis, R. Rosso, E.G. Virga, I. Mu\v{s}evi\{c},
% S. Kralj
%Theoretical and experimental study of the nanoparticle-driven blue phase
%stabilisation,
%\textit{Eur. Phys. J. E} \textbf{34}, 17 (2011).
%
\bibitem{dierking}
Dierking, I., et al.,
%I. Dierking, W. Blenkhorn, E. Credland, W. Drake, R. Kociuruba, B. Kayser,
%T. Michael,
Stabilising liquid crystalline blue phases,
\textit{Soft Matter} \textbf{8}, 4355--4362 (2012).
%
\bibitem{draper}
Draper, M., et al.
Self-assembly and shape morphology of liquid crystalline gold metamaterials,
\textit{Adv. Func. Mat.}, \textbf{21} 1260--1278 (2011).
%
\bibitem{milette2012}
Milette, J., et al.,
Reversible long-range network formation in gold nanoparticle-nematic
liquid crystal composites,
\textit{Soft Matter}, \textbf{8}, 173--179 (2012).
%
\bibitem{cordoyiannis} Cordoyiannis, G., et al.,
% G. Cordoyiannis, V.S.R. Jampani, S. Kralj, S. Dhara, V. Tzitzios,
% G. Basina, G. Nounesis, Z. Kutnjak, C.S.P. Tripathi, P. Losada-P\'{e}rez,
% D. Jesenek, C. Glorieux, I. Mu\v{s}evi\v{c}, A. Zidan\v{s}ek,
% H. Ameinitsch, J. Theon,
Different modulated structures of topological defects stabilized by adaptive
targeting nanoparticles,
\textit{Soft Matter} \textbf{9}, 3956--3964 (2013).
}

@@

\bibitem{deGennes}
\textcolor{red}{de Gennes, P.-G., and  Prost, J.,
{\it The Physics of Liquid Crystals} (Clarendon Press, 1995).}

@@

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{\textbf{Bulk blue phase structures.} Snapshots of the states
obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$;
(B,F) $w=0.23$ and $\phi=5\%$; 
(C,G) $w=2.3$ and $\phi=1\%$; and
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supplementary
Information.] For clarity, only a portion of the simulation box is shown
\textcolor{red}{its linear extent being $\simeq 28R$}
(one eighth of the total volume);
the full structures are shown in
Supplementary Figs.~2 and~3.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig2.jpg}}
\caption{\textbf{Confined blue phase structures.}
Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase is placed in a sandwich geometry, 
and then quenched into a regime where BPI is stable in the bulk. Both top and side views are provided.
The anchoring of the director field at the walls is normal for (A-D) and planar for (E-H). 
Structures correspond to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=2\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=2\%$.
As in Fig.~1, only one quarter of the simulation box is shown for clarity
\textcolor{red}{(its horizontal extent being $\simeq 56R$ and vertical
extent $\simeq 24R$ in the narrow direction)};
the full structures are shown in Supplementary Figs.~5 and~6.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.48\textwidth]{col_disc_x_run1267.png}
\includegraphics[width=0.43\textwidth]{sq_x_run1267.png}\\
\includegraphics[width=0.48\textwidth]{col_disc_x_run1341.png}
\includegraphics[width=0.43\textwidth]{sq_x_run1341.png}
\end{center}
\caption{\textbf{Structure in electric field.}
Steady states obtained when a dispersion of colloids is inserted
into a thermodynamically stable bulk BPIII with and without applied
external electric field. Panel A shows the situation in zero field, and panel
C the situation when the applied field is in the $x$-direction
(perpendicular to the plane of the paper). Panels B and D show one
plane of the three-dimensional structure factor $S(\mathbf{k})$ computed
from the positions of the particles, with wavevector $k_x = 0$, corresponding
to A and C respectively. With field, the disclinations form a honeycomb
pattern with hexagonal ordering perpendicular to the field direction;
this is reflected in the structure factor.
Simulations use weakly anchoring particles $w=0.23$, and a volume
fraction of $\phi=5\%$ (see Supplementary Information for full list of
parameters).
\textcolor{red}{The full simulation with a box size of $\simeq 56R$ is shown.}}
\end{figure}

>>>>

But one may also choose to disperse colloidal particles in a cholesteric, 
rather than nematic, liquid crystal. The molecules making up this material are
chiral, and this causes their average orientation (described by a director field) to rotate in space in
a helical fashion, rather than remain uniform as in nematics. 
This typically creates a 1-dimensional periodic structure, called the cholesteric phase, whose wavelength 
is the pitch, $p$. The periodicity can however become fully three dimensional in the so-called blue phases (BPs)~\cite{mermin}. BPs arise because the director field can twist around more than one direction at once (see 
the cartoon in Supplementary Fig.~1). Such double twist 
regions (generally cylinders) are energetically favoured at high enough molecular chirality, but
lead to geometric frustration because it is impossible to tile the whole 3D
space with double twist cylinders without also introducing ``disclination lines'' 
(These are singular topological defects on which the director field is 
undefined.) In blue phases these disclination lines themselves either form a 3D periodic regular lattice (in so called BPI and BPII), or remain disordered (BPIII)~\cite{bp3}. 
%
BPs are stabilised by the tendency of chiral molecules to twist, but destabilised by the cost of forming topological defects (which locally diminish the molecular alignment). In conventional cholesteric materials~\cite{mermin} this balance is only achievable in a narrow temperature range of a few degrees, around the onset of liquid crystalline ordering.
However, recent advances in formulation have widened this stability
range enormously~\cite{kikuchi,bplasers,coleswidetrange,bpdevice}. Most
recently, templated BPs with a stability range of -125
to~125$^\circ$C have been reported \cite{coles}, paving the way to
applications of BPs in operational display devices.

@@

The simulations presented here are representative of a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a diameter of around 50~nm. The simulations
address both the bulk structure, and the structure which forms when
the colloidal dispersion is confined in a narrow sandwich of width
comparable to the unit cell size~\cite{extrareference2}. It is seen
that a wide variety of structure is possible, and may be influenced
by parameters including the solid volume fraction, and the details
of the anchoring at the colloid surface (and the at the surface of the
confining walls). Further, evidence is found for metastable switching of
this structure in an applied electric field. Details of the
computational approach are set out in the Methods section, while
simulation parameters are reported in the Supplementary Information.

@@

\noindent
\textbf{Structure in bulk BPI.}
We show in Fig.~1 A-D the final state structures of four simulations in which we first equilibrated a stable BPI disclination network in bulk (with periodic boundary conditions) and then dispersed colloidal particles at random within it. Among dimensionless control parameters are the particle solid volume fraction $\phi$  ($\phi = 1\%$ or $5\%$); the ratio $r = R/\lambda$ of particle radius to the BP lattice parameter $\lambda$ (here $r\simeq 0.14$) and the ratio $w = WR/K$ where $W$ is the anchoring strength of the cholesteric at the particle surface, and $K$ is the elastic constant of the liquid crystal.
The anchoring strength is defined such that $W > 0$ imparts a preferred
orientation to the director field at the particle surface. This orientation
can be either normal to the surface or in a plane tangential to the surface,
a property related to surface chemistry in experimental systems.
We choose $w = 0.23, 2.3$ which are within typical experimental range~\cite{tiffany}. This parameter can be viewed as the ratio of the anchoring energy, $WR^2$, to the elastic energy scale for distortion~$KR$.

@@

As colloidal-nematic composites~\cite{tiffany}, all the structures in
Fig.~1A-D 
should be soft solids, of nonzero elastic 
modulus $G$ at low frequency. This contrasts with pure BPs, where
$G=0$ as the fluid can flow with a finite
viscosity via permeation of molecules through a fixed defect lattice~\cite{permeation1,permeation2}. We expect the
structures in Fig.~1A-C to be only weak gels, as here the 
defect network percolates but particle contacts do not. This is broadly similar to the cholesteric-nanoparticle gel reported
in~\cite{lubensky} (with $G<1$ Pa). In contrast, the colloidal gel
structure in Fig.~1D should be much more resistant mechanically, 
due to the formation of a thick percolating particle network. The 
structure is now akin to that of the self-quenched glass found in 
colloidal-nematic composites~\cite{tiffany} at much higher volume 
fraction (over 20\% as opposed to below 5\% here), for which $G\sim 10^3$ Pa.
This figure is consistent with an estimate obtained by comparing
the mechanical properties of the network of defects stabilised by
colloidal particles with those of rubber~\cite{ramos} for
the relevant simulation parameters (see Supplementary Information).

@@

\textcolor{red}{
It may be possible to anneal the structures obtained via the quench route,
although we have not attempted this in simulation. The results presented
suggest that even when starting with colloidal particles randomly dispersed
in an ordered blue phase, the particles are able to distort the structure
(Fig.~1A-B). This suggests that it would be difficult to identify a quench
protocol which would lead to less, rather than more, disorder.
}

@@

The degree of similarity between
the bulk and confined structures is somewhat masked by the local
change in particle density in the confined case. If one allows for
this, Figs.~1 and~2 show the individual structural motifs are actually
rather similar: templated lines for weak anchoring and clusters for
strong anchoring.

\medskip
\noindent
\textbf{Switching in electric field.}
An interesting question, relevant for applications to devices, is whether 
these structures can be modified, or switched, with electric fields.
Fig.~3 addresses this question, starting from amorphous Blue Phase III,
this time at a higher chirality. Dispersing colloidal particles in this
network
results in the particle occupying the available nodes, where the order
parameter is low (Fig.~3A; Supplementary Movie~5). Applying a high enough
field 
along the $x$ direction leads to a switching to a new phase, where colloidal 
arrays fit within a network with distorted hexagonal cells (Fig.~3B 
and Supplementary Fig.~7; Supplementary Movie~6). 
Remarkably, upon field removal this honeycomb structure does not find its 
way back to the 
configuration before switching on the field, but gets stuck into a metastable 
structure (Supplementary Fig.~7), with residual anisotropy along the field
switching 
direction. Cycling the field along the $x$ and $y$ directions leads to
distinct metastable structures, which are retained after field removal
(Supplementary Fig.~8 and Fig.~9).
\textcolor{red}{
We note that for the fluid parameters used here, the field induced
changes are irreversible with the weakly anchoring colloid particles.
The mesophase without colloid particles undergoes
a reversible ordering transition~\cite{bp3}; the reversibility
is retained in the
presence of particles only if their anchoring is very weak.}

@@

How do these simulations relate to experiment? Several authors have
used nanoparticles in the context of stabilising BPs
\cite{yoshida2009,karatairi}. These
nanoparticles are typically a few nanometres in size, in which case
stabilisation is explained by the mechanism of defect removal.
Experiments suggest this mechanism is also
relevant for larger particles in the range of 40--70~nm 
\cite{dierking}, which is consistent with the current simulations.
However, the mechanism is observed to be less efficient for
particles above 100~nm, where particles may start to disrupt
longer-range liquid crystal order \cite{dierking}. While the field of
self-assembly with nanoparticles is relatively new \cite{draper},
nanoparticles have also been used in both nematic \cite{milette2012}
and chiral liquid crystals \cite{cordoyiannis} as host fluid templates.
The variation of structure seen
in our simulations suggest that some careful characterisation of parameters
such as surface anchoring of particles (which are often stabilised, or even
functionalised with surface ligands), together with those associated
with any confining surfaces or interfaces, is required to understand the
final structure and to be able to reproduce it with a given experimental
protocol. The identification of a model system which could allow
unambiguous comparison between experimental systems and simulation
would be extremely useful. Such a system might adopt particles of
diameter in the range 50~nm or above, which allows a coarse-grained simulation
approach of the type used here to be adopted, which can then capture the
large-scale structure required to compare with experiment. In the same vein,
detailed surface chemistry is difficult to represent in coarse-grained
simulations, so heavily functionalised particles might be avoided.

@@

\medskip
\noindent
\textbf{Surface free energy.}
In addition to the fluid free energy density $f(Q_{\alpha\beta})$, a surface
free energy density is also present to represent the energetic cost of
anchoring at a solid surface.
\textcolor{red}{In the case of normal anchoring, the surface free energy
density (per unit area) is}
\begin{equation}
f_s(Q_{\alpha\beta}, Q^0_{\alpha\beta})
= {\textstyle \frac{1}{2}}W(Q_{\alpha\beta} - Q^0_{\alpha\beta})^2,
\end{equation}
\textcolor{red}{where $Q^0_{\alpha\beta}$ is the preferred order
parameter tensor at the solid surface, and $W$ is a constant determining
the strength of the anchoring. In the case of planar anchoring, a slightly
more complicated expression is required to allow for degeneracy
(see, e.g., \cite{fournier2005}.)}
The determination of $Q^0_{\alpha\beta}$ for normal and planar anchoring is
discussed below. For a colloidal particle of radius $R$, the strength of
the surface
anchoring compared which the bulk fluid elastic constant may be quantified
by the dimensionless parameter $WR/K$. For small values of this parameter,
the presence of a particle surface should have little impact on the local
fluid LC ordering.

@@

\bibitem{mermin} Wright, D.C., and Mermin, N.D.,
Crystalline liquids: the blue phases, {\it Rev. Mod. Phys.} {\bf 61},
385--432 (1989).

@@

\bibitem{extrareference1}
Ravnik, M., Alexander, G.P., Yeomans, J.M., and Zumer, S.,
Mesoscopic modelling of colloids in chiral nematics,
{\it Faraday Discuss.} {\bf 144}, 159--169 (2010).

@@

\bibitem{extrareference2}
Ravnik, M., Fukuda, J.-I.,  Yeomans, J.M., and Zumer, S.,
Confining blue phase colloids to thin layers,
{\it Soft Matter} {\bf 7}, 10144--10150 (2011).

@@

\bibitem{ramos} 
Ramos, L., Zapotocky, M.,  Lubensky, T.C., and  Weitz, D.A.,
Rheology of defect networks in cholesteric liquid crystals,
{\it Phys. Rev. E} {\bf 66} 031711 (2002).

@@

\bibitem{yoshida2009}
Yoshida, H., et al.,
Nanoparticle-stabilized cholesteric blue phases,
\textit{Appl. Phys. Express}, \textbf{2}, 121501 (2009).
%
\bibitem{karatairi} Karatairi, E., et al.,
% E. Karatairi, B. Ro\v{z}i\v{c}, Z. Kutnjak, V. Tzitzios, G. Nounesis,
% G. Cordoyiannis, C. Glorieux, J. Thoen, S. Kralj,
Nanoparticle-induced widening of the temperature range of
liquid-crystalline blue phases, 
\textit{Phys. Rev. E} \textbf{81}, 041703 (2010).
%
%\bibitem{rozic} B. Ro\v zi\v c,
% B. Ro\v{z}i\v{c}, V. Tzitzios, E. Karatairi, U. Tkalec, G. Nounesis,
% Z. Kutnjak, G. Cordoyiannis, R. Rosso, E.G. Virga, I. Mu\v{s}evi\{c},
% S. Kralj
%Theoretical and experimental study of the nanoparticle-driven blue phase
%stabilisation,
%\textit{Eur. Phys. J. E} \textbf{34}, 17 (2011).
%
\bibitem{dierking}
Dierking, I., et al.,
%I. Dierking, W. Blenkhorn, E. Credland, W. Drake, R. Kociuruba, B. Kayser,
%T. Michael,
Stabilising liquid crystalline blue phases,
\textit{Soft Matter} \textbf{8}, 4355--4362 (2012).
%
\bibitem{draper}
Draper, M., et al.
Self-assembly and shape morphology of liquid crystalline gold metamaterials,
\textit{Adv. Func. Mat.}, \textbf{21} 1260--1278 (2011).
%
\bibitem{milette2012}
Milette, J., et al.,
Reversible long-range network formation in gold nanoparticle-nematic
liquid crystal composites,
\textit{Soft Matter}, \textbf{8}, 173--179 (2012).
%
\bibitem{cordoyiannis} Cordoyiannis, G., et al.,
% G. Cordoyiannis, V.S.R. Jampani, S. Kralj, S. Dhara, V. Tzitzios,
% G. Basina, G. Nounesis, Z. Kutnjak, C.S.P. Tripathi, P. Losada-P\'{e}rez,
% D. Jesenek, C. Glorieux, I. Mu\v{s}evi\v{c}, A. Zidan\v{s}ek,
% H. Ameinitsch, J. Theon,
Different modulated structures of topological defects stabilized by adaptive
targeting nanoparticles,
\textit{Soft Matter} \textbf{9}, 3956--3964 (2013).

@@

\bibitem{deGennes}
de Gennes, P.-G., and  Prost, J.,
{\it The Physics of Liquid Crystals} (Clarendon Press, 1995).

@@

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{\textbf{Bulk blue phase structures.} Snapshots of the states
obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$;
(B,F) $w=0.23$ and $\phi=5\%$; 
(C,G) $w=2.3$ and $\phi=1\%$; and
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supplementary
Information.] For clarity, only a portion of the simulation box is shown
its linear extent being $\simeq 28R$
(one eighth of the total volume);
the full structures are shown in
Supplementary Figs.~2 and~3.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig2.jpg}}
\caption{\textbf{Confined blue phase structures.}
Snapshots of the steady states obtained when a dispersion of colloids in the isotropic phase is placed in a sandwich geometry, 
and then quenched into a regime where BPI is stable in the bulk. Both top and side views are provided.
The anchoring of the director field at the walls is normal for (A-D) and planar for (E-H). 
Structures correspond to (A,E) $w=0.23$ and $\phi=1\%$, 
(B,F) $w=0.23$ and $\phi=2\%$, 
(C,G) $w=2.3$ and $\phi=1\%$,
(D,H) $w=2.3$ and $\phi=2\%$.
As in Fig.~1, only one quarter of the simulation box is shown for clarity
(its horizontal extent being $\simeq 56R$ and vertical
extent $\simeq 24R$ in the narrow direction);
the full structures are shown in Supplementary Figs.~5 and~6.}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.48\textwidth]{col_disc_x_run1267.png}
\includegraphics[width=0.43\textwidth]{sq_x_run1267.png}\\
\includegraphics[width=0.48\textwidth]{col_disc_x_run1341.png}
\includegraphics[width=0.43\textwidth]{sq_x_run1341.png}
\end{center}
\caption{\textbf{Structure in electric field.}
Steady states obtained when a dispersion of colloids is inserted
into a thermodynamically stable bulk BPIII with and without applied
external electric field. Panel A shows the situation in zero field, and panel
C the situation when the applied field is in the $x$-direction
(perpendicular to the plane of the paper). Panels B and D show one
plane of the three-dimensional structure factor $S(\mathbf{k})$ computed
from the positions of the particles, with wavevector $k_x = 0$, corresponding
to A and C respectively. With field, the disclinations form a honeycomb
pattern with hexagonal ordering perpendicular to the field direction;
this is reflected in the structure factor.
Simulations use weakly anchoring particles $w=0.23$, and a volume
fraction of $\phi=5\%$ (see Supplementary Information for full list of
parameters).
The full simulation with a box size of $\simeq 56R$ is shown.}
\end{figure}
